### 2017-07-26 synthetic_experiments/long_experiments_summary.Rmd
add experiments on real data

```{r, echo = FALSE}
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
source(paste0(current_path, "run_from_data.R"))
source(paste0(current_path, "run_parallelized_from_data.R"))
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
library(ggplot2)
```

@@

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
source(paste0(current_path, "run_from_data.R"))
source(paste0(current_path, "run_parallelized_from_data.R"))
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
library(ggplot2)
library(ggjoy)
library(dplyr)
library(tidyr)
```

@@

## Joy Plots of Algorithm Sampling Choices

### Experiment 3

```{r, echo = FALSE}
load(file = paste0(current_path, "arm_seq_loc2.Rda"))

arm_seq_APT_loc2 %>% tbl_df() %>% 
  mutate(index = 1:2000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 10, index <= 1500) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
  labs(title = "APT")

arm_seq_BUCB_loc2 %>% tbl_df() %>% 
  mutate(index = 1:4000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 10, index <= 1500) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
  labs(title = "Bayes-UCB")

arm_seq_KLUCB_loc2 %>% tbl_df() %>% 
  mutate(index = 1:1500) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 10) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
  labs(title = "KL-UCB")

arm_seq_AugUCB_loc2 %>% tbl_df() %>% 
  mutate(index = 1:2000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 10, index <= 1500) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
  labs(title = "Augmented UCB")
```

### Experiment 3

```{r, echo = FALSE}
load(file = paste0(current_path, "arm_seq_loc3.Rda"))

arm_seq_APT_loc3 %>% tbl_df() %>% 
  mutate(index = 1:7000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 10, index <= 5000) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
  labs(title = "APT")

arm_seq_BUCB_loc3 %>% tbl_df() %>% 
  mutate(index = 1:7000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 10, index <= 5000) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
  labs(title = "Bayes-UCB")

arm_seq_KLUCB_loc3 %>% tbl_df() %>% 
  mutate(index = 1:5000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 10) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
  labs(title = "KL-UCB")

arm_seq_AugUCB_loc3 %>% tbl_df() %>% 
  mutate(index = 1:7000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 10, index <= 5000) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
  labs(title = "Augmented UCB")
```

### Experiment 4

```{r, echo = FALSE}
load(file = paste0(current_path, "arm_seq_loc4.Rda"))

arm_seq_APT_loc4 %>% tbl_df() %>% 
  mutate(index = 1:8000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 11) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
  labs(title = "APT")

arm_seq_BUCB_loc4 %>% tbl_df() %>% 
  mutate(index = 1:8000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 11) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
  labs(title = "Bayes-UCB")

arm_seq_KLUCB_loc4 %>% tbl_df() %>% 
  mutate(index = 1:8000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 11) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
  labs(title = "KL-UCB")

arm_seq_AugUCB_loc4 %>% tbl_df() %>% 
  mutate(index = 1:8000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 11) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
  labs(title = "Augmented UCB")
```

### Experiment 5

```{r, echo = FALSE}
load(file = paste0(current_path, "arm_seq_loc5.Rda"))

arm_seq_APT_loc5 %>% tbl_df() %>% 
  mutate(index = 1:8000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 10) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
  labs(title = "APT")

arm_seq_BUCB_loc5 %>% tbl_df() %>% 
  mutate(index = 1:8000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 10) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
  labs(title = "Bayes-UCB")

arm_seq_KLUCB_loc5 %>% tbl_df() %>% 
  mutate(index = 1:8000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 10) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
  labs(title = "KL-UCB")

arm_seq_AugUCB_loc5 %>% tbl_df() %>% 
  mutate(index = 1:8000) %>%
  gather(key = iter, value = arm, -index) %>%
  dplyr::filter(index > 10) %>%
  dplyr::group_by(arm, index) %>%
  dplyr::summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
  labs(title = "Augmented UCB")
```

```{r, echo = FALSE, include = FALSE}
arm_seq_APT_loc5 %>% tbl_df() %>% 
  mutate(index = 1:8000) %>%
  gather(key = iter, value = arm, -index) %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = index, y = arm)) +
  geom_joy(scale = 2) + theme_joy() +
  scale_y_discrete(expand = c(0.01, 0)) +
  scale_x_continuous(expand = c(0, 0)) +
  labs(title = "APT")

arm_seq_APT_loc5 %>% tbl_df() %>% 
  mutate(index = 1:8000) %>%
  filter(index <= 2000) %>%
  gather(key = iter, value = arm, -index) %>%
  filter(index %in% seq(11,4000, by = 100)) %>%
  mutate(index = as.factor(index)) %>%
  ggplot(aes(x = arm, y = index)) +
  geom_joy(stat = "binline", binwidth = 1, scale = 0.9) + theme_joy() +
  scale_y_discrete(expand = c(0.01, 0)) +
  scale_x_continuous(expand = c(0, 0)) +
  labs(title = "APT")
```

```{r, echo = FALSE}
load(file = paste0(current_path, "wrong_arms_BUCB_loc2.Rda"))
head(wrong_arms_BUCB_loc2,100)
wrong_arms_BUCB_loc2 %>%
  filter(!is.na(arm), round > 10) %>%
  group_by(round, arm) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(arm = as.factor(arm)) %>%
  ggplot(aes(x = round, y = arm, height = n)) +
  geom_joy(stat = "identity", scale = 1.8, size = 0.2) + theme_joy() +
  labs(title = "Bayes-UCB - Experiment 2")
```
